\plaintitle

### 2017-04-25 statistical-quorum.tex
New title.
Better title.
Initial introduction.

\documentclass{sigchi}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{PeerMind: Statistical Quorum}
%\def\plainauthor{First Author, Second Author, Third Author,
%  Fourth Author, Fifth Author, Sixth Author}
%\def\emptyauthor{}
%\def\plainkeywords{Authors' choice; of terms; separated; by
%  semicolons; include commas, within terms only; required.}
%\def\plaingeneralterms{Documentation, Standardization}

@@

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
%\bibliographystyle{sigchi}
%\bibliography{refs}

>>>>

\documentclass[chi_draft]{sigchi}

@@

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Using statistical quorum to improve legitimacy of decisions and utilization of collective attention in democratic communities}
%\def\plainauthor{First Author, Second Author, Third Author,
%  Fourth Author, Fifth Author, Sixth Author}
%\def\emptyauthor{}
%\def\plainkeywords{Authors' choice; of terms; separated; by
%  semicolons; include commas, within terms only; required.}
%\def\plaingeneralterms{Documentation, Standardization}

@@

Many democratic communities use voting to make collective decisions.
\todo{Should we support this statement with a reference?}
In its basic form voting consist of members of a community casting a vote \emph{in favor} or \emph{against} a decision and if
majority ($> 50\%$) of votes are in favor of the decision, the decision \emph{passes} and is adopted as a decision
of the whole community.

There have been many improvements proposed to this basic form and various analysis made.
\todo{Add references.}
In this paper we focus on the question of \emph{quorum} and how high the quorum should be.
Quorum is the minimum number of members participating in voting for voting to be seen as representative of the whole
community, i.e., legitimate.
If quorum is too low, decisions adopted might not represent the community.
If it is too high, the community might have issues achieving the quorum.
Not enough members might decide to participate in voting, or members might on purpose boycott voting to
prevent decision to be adopted, even if those opposing it are in minority.
Communities often decide quorum arbitrary\footnote{Robert's Rules of Order states that the quorum
``should approximate the largest number that can be depended on to attend any meeting except in very bad weather
or other extremely unfavorable conditions.''~\cite{roberts}}
and try to increase participation of members in communities' democratic processes.
\todo{Add references.}
Moreover, many democratic communities have issues achieving quorum which hinders their operation.
\todo{Add references.}

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{sigchi}
\bibliography{refs}
